\plaintitle

### 2017-01-09 drafts/labor/discussion.tex
added rosenberg refs in discussion

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past can't be a perfect predictor for the future;
as \citeauthor{scholz2012digital} points out,
``it would be wrong to conclude that
in the realm of digital labor
there is nothing new under the sun''
\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern on--demand work.
For example, unlike physical work environments, people can (and often do) contribute to online communities in a one--off manner
\cite{mcinnis2016one}.
The internet makes this kind of loose affiliation feasible.
While we have attempted to understand the likely overlaps and differences between history and modern day, no analysis is perfect.

@@

\msb{Shouldn't we bring up the discussion from the rebuttal about history/future connections here?}

@@

\topic{A uniquely challenging facet of this topic of inquiry is the public attention that this domain has attracted.}
Activists have described speculative work as having
``essentially been turned into modern--day slaves''~\cite{activistsHuffPoLawsuit}.
Meanwhile, advocates describe it as
``a project of sharing
aimed at providing ordinary people
with more economic opportunities and
improving their lives''~\cite{uberPropaganda}.

\topic{Piecework teaches us that, without appropriate norms and policy, the dystopian outcome has happened and will happen again.}
The piecework nature of on--demand work induces us
``to neglect tasks that are less easy to measure'' \cite{SJOE:SJOE371},
rewarding us not for creativity but predictability;
payment for this work may ultimately be determined by
an algorithm that fundamentally doesn't understand people;
the layers between us and our managers might increasingly become
``defective (simple, observable)'' algorithms \cite{10.2307/2555446},
just like those which already frustrate
on--demand workers
\cite{uberAlgorithm,dynamo,turkopticon}.
However, social policy has advanced since the early 1900s, so as on--demand work gains popularity a repeat of \textit{How the Other Half Lives}~\cite{riisOtherSideLives} seems less likely.

\topic{On the other hand, while piecework's nascent years were grim, 
they precipitated a century of extremely strong labor advocacy~\cite{hart2013rise,mccallum2013global}.}
Even today, the geist that came out of the labor union revolution
inspires collective action and worker empowerment around the world:
in India, workers across the nation recently engaged in
the largest labor strike in human history
--- perhaps as many as 150 million
\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to permeate on--demand labor markets as some have called for
\cite{futureUnions},
then the future of on--demand labor may follow
the same trajectory of worker empowerment that piecework \textit{later} found.

>>>>

\subsection{The Hazards of Predicting the Future}\label{sec:perilousProblemsPredicting}
The past isn't a perfect predictor for the future;
as \citeauthor{scholz2012digital} cautions,
``it would be wrong to conclude that in the realm of digital labor there is nothing new under the sun''~\cite{scholz2012digital}.
Our analysis is limited by the differences, foreseen and unforeseen, between historical piecework and modern on--demand work.
For example, unlike physical work environments, people can (and often do) make one--off contributions to online communities~\cite{mcinnis2016one}.
While we have attempted to identify all of the likely parallels and divergences between piecework and on--demand work,
we can't claim to have accounted for everything.

@@

\citeauthor{rosenberg1994exploring} and others have contributed substantially to the practice in part by clearly limiting the extent of their claims
--- only offering, for instance,
``to narrow our estimates and thus to concentrate resources in directions that are more likely to have useful payoffs''~\cite{rosenberg1994exploring}.
Using this approach,
our method of relating history to modern socio--technical systems may be
a useful tool for researchers attempting
to make sense of ostensibly new phenomena.
In other words, offering ``that past history is an indispensable source of information
to anyone interested in characterizing technologies''~\cite{rosenberg1982inside}.

% \msb{Shouldn't we bring up the discussion from the rebuttal about history/future connections here?}

@@

\topic{A uniquely challenging facet of this domain is the public attention that it has garnered.}
Activists have described speculative work as having
``essentially been turned into modern--day slaves''~\cite{activistsHuffPoLawsuit}.
Meanwhile, advocates have described it as
``a project of sharing aimed at providing ordinary people with more economic opportunities and improving their lives''~\cite{uberPropaganda}.

\topic{Piecework teaches us that, without appropriate norms and policies, the dystopian outcome has happened and may happen again.}
The piecework nature of on--demand work induces us
``to neglect tasks that are less easy to measure''~\cite{SJOE:SJOE371},
rewarding us not for creativity but predictability;
payment for this work may ultimately be determined by
algorithms that fundamentally don't understand people;
the layers between us and our managers might eventually become
``defective (simple, observable)'' algorithms~\cite{10.2307/2555446},
just like those which already frustrate
on--demand workers~\cite{uberAlgorithm,dynamo,turkopticon}.
However, social policy has advanced since the early 1900s, so as on--demand work grows, a repeat of \textit{How the Other Half Lives}~\cite{riisOtherSideLives} seems less likely.

\topic{On the other hand, while piecework's nascent years were grim, 
they precipitated a century of some of the most potent labor advocacy organizations in modern history~\cite{hart2013rise,mccallum2013global}.}
Even today, the \textit{geist} of the labor union revolution
inspires collective action and worker empowerment around the world:
Recently, in India, workers across the nation engaged in
the largest labor strike in human history
\cite{indiaStrikeRealNews}.
If labor advocacy groups can find ways to effect change in on--demand work as some have called for
\cite{futureUnions},
then the future of on--demand labor may follow
the same trajectory of worker empowerment that piecework saw.
